Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
update Figure 3

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.pdf}
\caption{DSVerifier Verification Flow.}
\label{DSVerifier_process}
\end{figure*}

@@

@@

\paragraph{Use of fixed-point computation in the program synthesis engine}
The program synthesis engine uses fixed-point arithmetic,
therefore we need to examine the effect of discretization during these operations.
Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using Fixed-Point bit vectors with integer size $I_b$ and fractional
size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant $\hat{G}(z)$, and a discretizing function
\begin{align}
\small
\label{FWL_tf}
&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
\end{align}
we calculate $\tilde G(z)=f(\hat{G}(z))$
\begin{align}
% \label{digital_controller_tf}
% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
\end{align}
where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
denoted by $\mathfrak{G}(z)$.

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses BMC to 
compute a solution ($N_c$,$D_C$). % An important remark is that this 
% controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
% domain.

There are two approaches for the {\sc verify} phase based on the
described model.  The first uses interval arithmetic, representing the
coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$
and rounding operations outwards during the process. 
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insuficient.  Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
In our experimental section Sec.~\ref{sec:experiments}, we 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

In Fig.~\ref{fig:CEGIS}, we illustrate the second approach, which 
uses a two-stage verification. 
First, in the {\sc Uncertainty} sub-phase, assuming the 
current precision \param{I_b}{F_b},
we check whether 
the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

If the result of the {\sc Uncertainty} verification is that
the system is stable for the current candidate solution,
then we pass this solution to the {\sc Precision} verification sub-phase, 
which checks the propagation of the error in the fixed-point 
calculations using a Fixed-point Arithmetic Verifier based on 
interval arithmetic. 
%
% To achieve this, we use a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program. 
%
% The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples. The second phase verifies the propagation of the error in the fixed point calculations.
% If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution. 
% vouches for the use of CEGIS in most of our benchmarks.
% \cdsay{end of integration}

If this check returns $false$, then we 
increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
with an empty {\sc inputs} set.
Otherwise, we found a full solution for our synthesis problem
and we are done.

@@

 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). 
\label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation} \label{sec:experiments}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{DSVerifier Verification Flow.}
\label{DSVerifier_process}
\end{figure*}

@@

\textcolor{red}{Pascal: can you please update this section to include the CEGIS step?}

@@

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses a BMC-based verifier to 
compute a solution ($N_c$,$D_C$). An important remark is that this 
controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain.
A second remark is that the synthesis and verification engines use fixed/floating point arithmetic,
therefore we also need to examine the effect of discretization during these operations.
\cdsay{integrate the following with Dario}
Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using Fixed-Point bit vectors with integer size $I_b$ and fractional
size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
\begin{align}
\small
\label{FWL_tf}
&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
\end{align}
we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
\begin{align}
\label{digital_controller_tf}
\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
\end{align}
where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
denoted by $\mathfrak{G}(z)$.

The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program. The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples. The second phase verifies the propagation of the error in the fixed point calculations. If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution. The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
\cdsay{end of integration}

In the {\sc verify} phase, we have a two-step process. 
First, in the {\sc Uncertainty} sub-phase, assuming the 
current precision \param{I_b}{F_b},
we check whether 
the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

If the result of the {\sc Uncertainty} verification is that
the system is stable for the current candidate solution,
then we pass this solution to the {\sc Precision} verification sub-phase, 
which checks the propagation of the error in the fixed-point 
calculations. If this check returns $false$, then we 
increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
with an empty {\sc inputs} set.
Otherwise, we found a full solution for our synthesis problem
and we are done.

@@

 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). \label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation}
